Your Paper Title

### 2025-03-31 paper/paper.qmd
remove unused model data script and refine introduction in paper

    The annual blooming of cherry blossoms (Prunus species, more commonly known as sakura) represents not only a culturally significant event across many East Asian countries but also serves as a valuable biological indicator of climate patterns and changes; particularly, the tradition of hanami (flower viewing) dates all the way back to the Heian period in Japan. This paper will examine the statistical relationship between temperature fluctuations and the timing of sakura flowering dates, a connection that has gained increased scientific attention as global climate change accelerates. Historical records of cherry blossom flowering, some dating back several centuries in Japan, provide an exceptionally rare long-term dataset for analyzing phenological responses to temperature variations [@Aono2008]. By quantifying this relationship through robust statistical methods, we aim to contribute to the growing body of research on biological responses to climate change while also contextualizing the potential cultural impacts of shifting bloom times. The preservation of these iconic natural events holds both scientific value for understanding ecosystem responses to warming trends and cultural significance for communities where cherry blossom festivals represent important economic and social traditions.

>>>>

    The annual blooming of cherry blossoms (Prunus species, more commonly known as sakura) represents not only a culturally significant event across many East Asian countries but also serves as a valuable biological indicator of climate patterns and changes; particularly, the tradition of hanami (flower viewing) dates all the way back to the Heian period in Japan. This paper will examine the relationship between temperature fluctuations and the timing of sakura flowering dates, a connection that has gained increased scientific attention as global climate change accelerates. Historical records of cherry blossom flowering, some dating back several centuries in Japan, provide an exceptionally rare long-term dataset for analyzing phenological responses to temperature variations [@Aono2008]. By quantifying this relationship through robust statistical methods, we aim to contribute to the growing body of research on biological responses to climate change while also contextualizing the potential cultural impacts of shifting bloom times. The preservation of these iconic natural events holds both scientific value for understanding ecosystem responses to warming trends and cultural significance for communities where cherry blossom festivals represent important economic and social traditions.
